Generating Images From Captions\\ With Attention

### 2015-11-05 supp.tex

Each parameter in alignDRAW was initialized by sampling from a Gaussian distribution with 
mean $0$ and standard deviation $0.01$. The model was trained using \textit{RMSprop} with an initial learning rate of $0.001$. The norm of the gradients was clipped at a maximum of $10.0$ during training to deal with exploding gradients. We used a vocabulary size of $K = 25323$ and $K = 22$ for Microsoft COCO and MNIST with Captions respectively. All capital letters in the words were converted to small letters as a preprocessing step. For all tasks, $\overrightarrow{h}^{lang}_{n}$ and $\overleftarrow{h}^{lang}_{n}$ in the language model had $128$ units. The parameters in the \textit{align} operator had a dimensionality of $l = 512$, $\vv \in \mathbb{R}^{512}$, $U \in \mathbb{R}^{512 \times 128}$, $W \in \mathbb{R}^{512 \times n^{gen}}$ and $b \in \mathbb{R}^{512}$. For the Microsoft COCO task, the alignDRAW model was trained for $18$ epochs and the learning rate was reduced by the factor of $0.1$ after $11$ epochs. The architectural configurations of alignDRAW models are shown on Table~\ref{tab:drawhyper}.

>>>>

Each parameter in alignDRAW was initialized by sampling from a Gaussian distribution with 
mean $0$ and standard deviation $0.01$. The model was trained using \textit{RMSprop} with an initial learning rate of $0.001$. The norm of the gradients was clipped at a maximum of $10.0$ during training to deal with exploding gradients. We used a vocabulary size of $K = 25323$ and $K = 22$ for Microsoft COCO and MNIST with Captions respectively. All capital letters in the words were converted to small letters as a preprocessing step. For all tasks, $\overrightarrow{h}^{lang}_{n}$ and $\overleftarrow{h}^{lang}_{n}$ in the language model had $128$ units. The parameters in the \textit{align} operator had a dimensionality of $l = 512$, $\vv \in \mathbb{R}^{512}$, $U \in \mathbb{R}^{512 \times 256}$, $W \in \mathbb{R}^{512 \times n^{gen}}$ and $b \in \mathbb{R}^{512}$. For the Microsoft COCO task, the alignDRAW model was trained for $18$ epochs and the learning rate was reduced by the factor of $0.1$ after $11$ epochs. The architectural configurations of alignDRAW models are shown on Table~\ref{tab:drawhyper}.
